Figures

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
avoid label and cluster tree cutoff

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
```

>>>>

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7, cellwidth = 7)
```
